---
title: "Forest Plot"
author: "Hsuan-Chun Lin"
date: '2021-12-07'
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Source code to plot a Forest Plot
### Import necessary packages
```{r}
library(ggplot2)
library(plyr)
library(lattice)
library(forestplot)
```
### Import data
```{r}
data<-read.csv("demo.csv")
print(data)
```

### Assign values from specific columns for your forest plot
```{r}
cochrane_from_rmeta <- 
  structure(list(
    mean = c(data$HR),
    lower = c(data$LOWER),
    upper = c(data$UPPER)),
    .Names = c("mean", "lower", "upper"), 
    row.names = c(NA, -(length(data$HR))), 
    class = "data.frame")

tabletext<-cbind(data$Group, data$VALUE)
```

### Set the format parameters
- xlab_text:Set text content of x label.
- xrange(a, b, by = c) : here a is the lower limit, b is the upper limit, and
c is the interval of of x axis.
- fontsize: set the size of the fonts in the plot.
- boxsize: set the circle size which indecates the mean value of the plot. 
```{r}
#Setting parameters
xlab_text = "aHR (95% CI)" #Set x label
xrange = seq(0.9, 1.2, by=0.05)

#Set fontsizes
fontsize_lab = 1.0 #label
fontsize_xlab = 1.2 #label of x axis
fontsize_ticks = 0.9 #ticks of x axis

#Set box size
boxsize = 0.1

#Set colors
boxcolor = "red"
textcolor = "black"
linecolor = "steelblue" #for the line of each sample
labelcolor = "darkgreen" #color of label text
axiscolor = "green"
colorlabel = "orange"
hrelcolor = "black"
```
### Visualization

```{r}
#Generate forestplot
forestplot(tabletext,
           line.margin =0.0000001,
           cochrane_from_rmeta,
           new_page = TRUE,
           xlog=FALSE,
           boxsize=boxsize,
           col.lab=colorlabel,
           #is.summary=c(TRUE,TRUE,rep(FALSE,8),TRUE,rep(FALSE,7),TRUE,rep(FALSE,6),TRUE,rep(FALSE,5),TRUE,rep(FALSE,4),TRUE,rep(FALSE,3),TRUE,rep(FALSE,2)),
           is.summary = rep(FALSE, length(data$HR)), #Set which one is summary
           #xlog=TRUE,
           xlab=xlab_text,
           txt_gp = fpTxtGp(label =gpar(fontfamily = "Arial", cex=fontsize_lab,col=labelcolor),
                            xlab = gpar(fontfamily = "Arial", cex=fontsize_xlab,col=axiscolor),
                            ticks = gpar(fontfamily = "Arial", cex=fontsize_ticks)),
           col=fpColors(box=boxcolor,line=linecolor,text=textcolor),
           xticks = xrange,
           zero = 1,
           fn.ci_norm = fpDrawCircleCI, #Change the mark to circle
           ci.vertices = TRUE,
           ci.vertices.height = 0.1,
           hrzl_lines = list("2" = gpar( col = hrelcolor)))
```
